### 2015-11-18 section/3_redundancy.tex
finish section 3 roughly

\paragraph{Example}
Figure \ref{fig:Apache34464} shows a simplified code-snippet from Apache. 
It contains a cross-loop redundant bug --- 
the \texttt{for} loop starting on line 7 could be executed for many times,
applied to many \texttt{source} strings slightly different from each other
with a lot of
redundant computation.
Below, we use it to demonstrate how we identify \texttt{input}s.

@@

In practice, we rarely see cases where different loop 
instances are doing exactly the same computation.
For example, Figure~\ref{fig:Mozilla477564} demonstrates a cross-loop redundancy
problem in Mozilla. Here, the
latter instances contain more iterations than previous instances. 
Figure~\ref{fig:Apache34464} shows an example in Apache, 
The inner loop, which starts from line 9,  
searches from the beginning of a string \texttt{sb} for a target sub-string 
\texttt{s}. Since the outer loop, which starts on line 36, appends one 
character to \texttt{sb} in every iteration, every inner loop instance is 
doing computation that is similar, but not exactly the same, 
from its previous instance.

@@

First, we identify and avoid monitoring memory reads whose return values can be 
statically proved to
not change throughout one loop instance (i.e., for cross-iteration
redundancy analysis) or multiple loop instances (i.e., for cross-loop redundancy
analysis). Since we implement \Tool at LLVM byte-code level, a major part of this
analysis is already done by LLVM, which lifts loop-invariant memory
accesses out of loops. The only extra analysis we did is to 
prune memory reads whose reading address is loop invariant, and there are no writes 
inside the loop which are possibly conducted on the same address. 
For example, the read address of \texttt{aNode.localName} and \texttt{aNode.namespaceURI}
in Figure~\ref{fig:Mozilla477564} is loop-invariant, and there are no write conducted 
on the same address. We do not need to record these two memory read. 
%It is easy to lift read from local variable outside the loop. 
%Compiler is conservative to move read, which may cause exception, outside the loop.
%I think this part of analysis is to prune memory read which is invariant, but unsafe to be moved out by compiler. 
%llvm is very conservative to move memory read from array/structure/global variable/heap variable
%outside the loop.
%what we do is if the read address is loop invariant, and there are no other write possibly 
%write to the same place, we will not record the memory read.

%TODO: Linhai, I don't understand your original writing. Pls rephrase, and provide
%an toy example.
%For each monitored memory read, we use loop-invariant analysis to identify 
%whether the read address is loop-invariant. 
%If the address is invariant, and there are no memory writes whose addresses 
%may/must alias to the read address, we will not instrument the memory read.

@@

Second, we identify and avoid monitoring some memory reads whose return values 
can be statically proved to be different throughout one loop instance in 
cross-iteration redundancy analysis.
Specifically, for read on loop induction variable, such as i for loop at line 12 of Figure~\ref{fig:Apache34464}, 
%Specifically, reading of loop induction 
%variables, such as XXX, are always identified as source instructions in % variable i for loop at line 12
%cross-iteration redundancy analysis; 
we also know for sure that their return
values are different in different iterations. 
If source instructions include read on loop induction variables, we know that 
there could not be cross-iteration redundancy. 
We use scalar evolution analysis
provided by LLVM to identify induction variables and avoid tracking their
values.
%induction variables are not always identified as source instructions.
%it could be possible that side-effect instructions do not depend on induction variables.
%for example, side-effect instruction may only depend on array content, and array index 
%will not be source instructions

@@

Third, sometimes we only record the memory-address range of a sequence of memory
read, instead of the value returned by every read, in cross-loop redundancy
analysis. 
The loop at line 12 in Figure~\ref{fig:Apache34464} shows an example.
The content of array \texttt{source} is never modified
throughout the outer-loop, which starts 
at line 12 in the Figure~\ref{fig:Apache34464}.
%We do not have the static analysis to prove the content of array does not change.
%for source[i] for the loop at line 12, we only need to record source, initial value of i and final value of i. 
%TODO
%Do you really do analysis to prove that the source array is not changed?
%ANSWER
%Shan, I do not have invariant analysis to prove the the source array is not changed.
%I remove that part of writing in the last version I sent to you. 
%It is very difficult to implement the invariant analysis.
%I plan to discuss this in limitation part of this section, and say that this could bring false positives.
%There are reasons why I feel it is too difficult to implement the invariant analysis:
%1. it is difficult to find the range (the outer loop) to apply the analysis.
%assume we have loopA, loopB and loopC. loopA contains loopB, and loopB contains loopC. 
%we are analyzing loopC. It could be possible that loopB only execute 1 or 2 iterations, and loopA is the real outer loop
%2. It is very difficult to prove that there is no other loop inside the outer loop which does not write to the same array.
%There could be cases like:
% for(i = 0; i < 10; i++)
%   func(&(A[i]));
% func will write to its parameter.
Therefore, to check whether different inner loop instances read similar
sequence of array data, we only need to record the starting and 
ending array index touched by each inner loop, significantly reduce the 
monitoring overhead. To accomplish this optimization, we again leverage
the scalar evolution analysis provided by LLVM. The scalar evolution analysis
tells us whether the address of a memory read instruction
is a loop induction variable. For example, the address for memory read \texttt{source[i]} is added by one in each loop iteration,
so it is a loop induction variable. 
From the scalar evolution analysis, we know that the starting address is \texttt{source} plus the initial value of \texttt{i}, and the ending address
is source plus the ending value of \texttt{i}.  
%TODO Linhai, I don't understand your original text. The address is 
%source+i; loop induction variable is i. What do you mean by "the read address
%is an induction variable"? Please rewrite.

@@

For cross-iteration redundancy, batching is often used for
I/O related operations.
Therefore, we treat I/O related redundancy separately.
Specifically, when the only side effect of a loop is I/O operations
and the same statement(s) is executed in every loop iteration, we report this
as I/O related redundancy problem and suggest batching as a potential fix
strategy.

For cross-loop redundancy, whether to use memoization or batching often
depends on which strategy is cheaper to use. \Tool uses a simple
heuristic. If 
the side effect of each loop instance is to update 
a constant number of memory locations, like the 
buggy loop in Figure~\ref{fig:Mozilla477564} and Figure~\ref{fig:Apache34464}, 
we recommend memoization. Instead, if the side effect is to update
a sequence of memory locations, with the number of locations increasing
with the workload, memoization is unlikely to help save much computation and
hence batching is suggested.

%we xxx
%TODO

%%if side effect of the loop is to define several scalar value used outside the loop, we recommend memoization.
%%if side effect is to write to distinct memory address or conduct system call, 
%%we recommend batch

>>>>

\paragraph{Example}
Figure \ref{fig:Apache34464} shows a simplified code-snippet from Apache,
containing a cross-loop redundancy bug. 
The \texttt{for} loop starting on line 7 
searches a string \texttt{source} for a target sub-string 
\texttt{target}. Since the outer loop, which starts on line 2, appends one 
character to \texttt{source} in every iteration (line 30), 
every execution of the \texttt{for} loop is working on a similar 
\texttt{source} string from its previous execution, with a lot of redundancy. 
%applied to many \texttt{source} strings slightly different from each other
%with a lot of
%redundant computation.
%We use it to demonstrate how we identify \texttt{input}s below.

@@

In practice, we rarely see cases where different loop 
instances are doing exactly the same computation.
In cross-loop redundancy examples shown in 
Figure~\ref{fig:Mozilla477564} and
Figure~\ref{fig:Apache34464}, each loop instance is doing similar, but not
exactly the same, work from its previous instance.

@@

First, we identify and avoid monitoring memory reads whose return values can be 
statically proved to
not change throughout one loop instance
or multiple loop instances. 
Since we implement \Tool at LLVM byte-code level, the majority of this
analysis is already done by LLVM, which lifts loop-invariant memory
accesses out of loops. 
For example, the read of \texttt{max} on line 12 of 
Figure \ref{fig:Apache34464} is an \textit{input} instruction of the 
\texttt{while} loop on the same line. LLVM identifies it as a loop invariant
and lifts the read of \texttt{max}
out of the loop. Consequently, \Tool only records
its value once during each loop, not each iteration.
However, LLVM does not apply its loop-invariant analysis to heap and global
variables, so \Tool conducts some extra analysis --- it identifies those
memory reads \texttt{read(v)}, where the address of \texttt{v} 
is a loop invariant and no instructions 
inside the loop can possibly write to that address. 
For example, \Tool can identify that the values of
\texttt{aNode->localName} and \texttt{aNode->namespaceURI} do not change
throughout one loop instance
in Figure~\ref{fig:Mozilla477564}. This analysis is sound but not complete.
\Tool may miss some loop invariants.

Second, we leverage the scalar evolution analysis in LLVM to remove the 
monitoring to some loop-induction related variables.
The scalar evolution analysis can tell which variables are
loop-induction variables (e.g., \texttt{i} on line 10
of Figure~\ref{fig:Apache34464}) and what are their strides. 
We then use this information in two ways. 
One is for cross-iteration redundancy checking.
If a loop iteration's \texttt{input} set contains a loop-induction
variable, we know different iterations' inputs would be different and 
hence conclude that there is no cross-iteration redundancy without any
run-time analysis. 
The other is for cross-loop redundancy checking.
When the address of a memory read is a loop induction variable, such as
\texttt{source[i]} on line 10 of Figure~\ref{fig:Apache34464},
we only record the address range at run time (i.e., the start and the
end), instead of every value returned by the memory read.
Of course, this optimization could lead to false positives, reporting
non-redundant loop computation as redundant.
This may happen when the corresponding
memory locations are modified across different loop instances.
In that case, although different loop instances work on variables read from
similar memory locations, the values they read are different.

For cross-iteration redundancy, batching is often used for
I/O operations.
Therefore, we treat I/O related redundancy separately.
When the only side effect of a loop is I/O operations
and the same statement(s) is executed in every loop iteration, we report this
as I/O related redundancy problem and suggest batching as a potential fix
strategy.

For cross-loop redundancy, whether to use memoization or batching often
depends on which strategy is cheaper. \Tool uses a simple
heuristic. If 
the side effect of each loop instance is to update 
a constant number of memory locations, like the 
buggy loop in Figure~\ref{fig:Mozilla477564} and Figure~\ref{fig:Apache34464}, 
we recommend memoization. Instead, if the side effect is to update
a sequence of memory locations, with the number of locations increasing
with the workload, memoization is unlikely to save much and
hence batching is suggested.

%TODO what does batching mean for cross-loop redundancy???

\comment{
%%if side effect of the loop is to define several scalar value used outside the loop, we recommend memoization.
%%if side effect is to write to distinct memory address or conduct system call, 
%%we recommend batch

%It is easy to lift read from local variable outside the loop. 
%Compiler is conservative to move read, which may cause exception, outside the loop.
%I think this part of analysis is to prune memory read which is invariant, but unsafe to be moved out by compiler. 
%llvm is very conservative to move memory read from array/structure/global variable/heap variable
%outside the loop.
%what we do is if the read address is loop invariant, and there are no other write possibly 
%write to the same place, we will not record the memory read.

@@

%induction variables are not always identified as source instructions.
%it could be possible that side-effect instructions do not depend on induction variables.
%for example, side-effect instruction may only depend on array content, and array index 
%will not be source instructions

@@

%TODO Linhai, I don't understand your original text. The address is 
%source+i; loop induction variable is i. What do you mean by "the read address
%is an induction variable"? Please rewrite.

@@
